---
title: "NCBI rentrenz walkthrough"
author: "Caleb Paslay"
date: "`r Sys.Date()`"
output: 
html_document: cerulean
---

### What is the problem and the potential solution? 

**[AMV](https://www.ncbi.nlm.nih.gov/nuccore/?term=alfalfa+mosaic+virus)**

**[AMV complete](https://www.ncbi.nlm.nih.gov/nuccore/?term=alfalfa+mosaic+virus+complete)**


### Goals for this presentation
1. Introduction to terms used in rentrez to isolate various search parameters.
2. Fetching and summarizing information
3. Plotting the data.  

### Installation and loading 

```{r message=FALSE}
library(rentrez)
library(tidyverse)
library(ggplot2)
library(glue)
```

```{r}
entrez_dbs()
```

```{r}
entrez_db_summary(db = "pubmed") #summary of this specific database
```

```{r message=FALSE}
entrez_db_summary(db = "nuccore") #summary of this specific database
```

```{r}
entrez_db_links(db = "pubmed") #shows us links to other databases
```

```{r}
entrez_db_links(db = "nuccore") #shows us links to other databases
```

```{r}
entrez_db_searchable("pubmed") #set a search terms that can be used with a database
```

```{r}
AMV_search <- entrez_search(db = "nuccore", 
                            term = "alfalfa mosaic virus", retmax = 20)
```

```{r echo=FALSE, message=FALSE}
year <- 1950:2022 #Creating a range from 1950:2022
alfalfa_search <- glue("alfalfa mosaic virus[TITL]) AND {year}[PDAT]")


tibble(year = year,
       alfalfa_search = alfalfa_search) %>% 
  mutate(alfalfa= map_dbl(alfalfa_search, ~entrez_search(db="pubmed",
                                                           term = .x)$count))
       
search_count <- tibble(year = year,
                       alfalfa_search = alfalfa_search) %>% 
  mutate(alfalfa = map_dbl(alfalfa_search, ~entrez_search(db="pubmed",
                                                        term = .x)$count))

search_count %>% 
  ggplot(aes(x= year, y = alfalfa))+
  theme_bw() +
  geom_line(color = "blue",
            size = 2)

```

### Excercises 
1. Create a search of a topic, organism, etc.  
2. Use the summary or fetch arguement to extract relavent information to your search.  
3. Create a plot to see how this topic has been reported on over a particular time span.  



### Here are some helpful links if you would like to investiage this package more!

[rentrez guidlines](https://cran.r-project.org/web/packages/rentrez/vignettes/rentrez_tutorial.html) 

[rentrez pdf](https://cran.r-project.org/web/packages/rentrez/rentrez.pdf) 

[rentrez in practice](https://docs.ropensci.org/rentrez/) 


