```{r message=FALSE}
library(ggplot2)
library(patchwork)
library(ggthemes)
library(readr)
library(tidyverse)
```

### 1. Using my ebird dataset (https://github.com/mbtoomey/Biol_7263/blob/main/Data/MBT_ebird.csv?raw=true) First calculate the total number of species seen each month of each year in each location. Then plot the number of species seen each month with the color of the points indicating year and facet this plot by location.

```{r message=FALSE}
MBT_ebird <- read_csv("https://github.com/mbtoomey/Biol_7263/blob/main/Data/MBT_ebird.csv?raw=true")
```


```{r message = FALSE}
count_bird <- MBT_ebird %>% 
  select(common_name, month, year, location, count) %>% 
  group_by(location, common_name, month, year, count) %>% 
  summarise(location)
```

```{r}
plot_1 <- ggplot(data = count_bird) +
  aes(month, count) +
  geom_point(aes(color = year), size = 1)+
  facet_wrap(~location) +
  xlab("month") +
  ylab("number of species")+
  ggtitle("Birds") 
# I could not get this to work with my data. I tried a lot of different ways, but 
# was not successful... :(
```

Using the dataset from Assignment #5:

### 2. Plot a comparison of mass by treatment including the individual observations, the mean, and standard error of the mean. Use point color or shape to indicate the sex.

```{r}
assignment5_3 <- read_csv("Data/tidy_data.csv")

#First way I tried (using some of Madison's notes)
plot_2 <- ggplot(assignment5_3, 
                 aes(x = test, mass))+
  geom_jitter(aes(col = sex), size =2, na.rm = TRUE)+
  stat_summary(fun = mean, geom = "crossbar", width = 0.5, color = "green") +
  stat_summary(geom = "errorbar", width = 0.3) +
  xlab("Test Group")+
  ylab("Mass")+
  theme_bw()
plot_2

#Second way I tried (using some of Cari's notes)
plot_2.1 <- ggplot(assignment5_3, 
                       aes(x = test, y = mass, fill = sex)) +
  geom_boxplot()+
  theme_bw()
plot_2.1
```

### 3. Generate a scatter plot of age and mass, indicate treatment with point shape or color, and fit separate regression lines (without CI) to each treatment.

```{r}
plot_2.2 <- ggplot(assignment5_3, 
                   aes(x = age, y = mass, color= test,na.omit =TRUE))+
  geom_point(size = 2)+
  geom_smooth(method = "lm", se = FALSE)+
  labs(x="Age", y="Mass")+
  theme_bw()

plot_2.2
```

### 4. Combine the plots from 2 and 3 using patchwork tag each panel with and number or letter and include a title for the overall plot.

```{r}
combined_plot <- plot_2 / plot_2.2

combined_plot2 <- combined_plot + plot_annotation("Distribution of various data points", 
                                tag_levels = "A", caption = "Figure 1")
combined_plot2
```

### In an Rmarkdown document present your code with the figures generated inline.

#### **[My Script](ggplot_assignment_6_script.R)**