```{r}
library(tidyverse) #load the required packages
library(dplyr)
library(readr)
```

### 1. Pivot and merge these two data sets into a single tidy tibble. Export this tibble as a .csv file saved to a folder called “Results” folder within your R project.

```{r part 1}
part_1 <- read.csv("https://raw.githubusercontent.com/mbtoomey/Biol_7263/main/Data/assignment6part1.csv")
colnames(part_1)

part_1_1 <-  pivot_longer(part_1, cols = 2:21, names_to = c("sample_id", "sex", "test"), names_sep = "_")

part_1_2 <- pivot_wider(part_1_1, names_from = ID, values_from = value)
```

#### **[Part 1 : Pivot](Data/part1_pivot.csv)**

```{r part 2}
part_2 <- read_csv(file = "https://raw.githubusercontent.com/mbtoomey/Biol_7263/main/Data/assignment6part2.csv")

part2_1 <- pivot_longer(part_2, cols = 2:17, 
                        names_to = c("sample_id", "test"), 
                        names_sep = "\\.")  #\\ are needed for R to recognize the period (thanks Amy!)
part_2_2 <- pivot_wider(part2_1, names_from = ID, values_from = value)
```

#### **[Part 2: Pivot](Data/part_2_pivot.csv)**

```{r merging data}
## Merging data (trying inner join)
part_1_2 %>% 
  inner_join(part_2_2, by = c("sample_id", "test"))
# I was able to merge, but could not figure out how to keep, 
# Sample 1 and Sample 2 in the final merge. 

# Merging data (using full join function)
part_1_2 %>% 
  full_join(part_2_2, by = c("sample_id", "test")) 
```

#### **[Part 3: Merging the two data tables](Data/tidy_data.csv)**

### 2. With this tidy tibble, generate a new tibble of the mean +/- standard deviation of the residual mass (mass/body length) by treatment and sex. Export this tibble as a .csv file saved to a folder called “Results” folder within your R project.

```{r}
tidy_data <- read_csv("Data/tidy_data.csv")
```


```{r}

tidy_data %>% 
  mutate(residual_mass = mass / body_length) %>% 
  select(test, sex, residual_mass) %>% 
  group_by(test) %>%
  summarize(mean_mass=mean(residual_mass, na.rm=TRUE), #removing NA's is important here.
            SD_mass=sd(residual_mass, na.rm=TRUE)) %>% 
  write.csv("Data/mean_&_SD.csv")
```

#### **[Part 4: Summarizing data](Data/mean_&_SD.csv)**

### 3. In an Rmarkdown document present the code you used to pivot, merge, etc. and the links to the commented R script and final .csv files stored in your Data folder. Knit this to an html file and link on your portfolio page.

#### **[My R Script](tidyr_exercise.R)**


